Learning to Pivot with Adversarial Networks

### 2017-05-18 tex/nips/nips_2017.tex
another grammatical fix
typos

\begin{abstract}
Several techniques for domain adaptation have been proposed to account for differences in the
distribution of the data used for training and testing. The majority of this work focuses on
a binary domain label. Similar problems occur in a scientific context where there may be a continuous family of
plausible data generation processes associated to the presence of systematic uncertainties. 
Robust inference is possible if it is based on a
    pivot -- a quantity whose distribution does not depend on the unknown value of the
    nuisance parameters that parametrize this family of
    data generation processes. In this work,  we introduce and derive theoretical results
     for ta training procedure
    based on adversarial networks for enforcing the pivotal property (or, equivalently, fairness with respect to continuous attributes) on a predictive model.
    The method includes a hyperparameter, which one can tune a trade-off between accuracy and robustness. We
    demonstrate the effectiveness of this approach with a toy example and an examples
    from particle physics.
\end{abstract}

@@

In terms of applications, the proposed solution can be used in any situation
where the training data may not be representative of the real data the
predictive model will be applied to in practice. In the scientific context, the
presence of systematic uncertainty can be incorporated by considering a family
of data generation processes, and it would be worth revisiting those scientific problems
that utilize machine learning in light of this technique. Moreover, the approach
also extends to cases where independence of the predictive model with respect to
observed random variables is desired, as in domain adaptation or fairness in
classification (e.g. \citep{Shimmin:2017mfk}).
% not sure this is a great sentence to end with, sounds like a sales pitch
% Again, trying our algorithm on these use cases is certainly
%worth investigating.

>>>>

\begin{abstract}

Several techniques for domain adaptation have been proposed to account for
differences in the distribution of the data used for training and testing. The
majority of this work focuses on a binary domain label. Similar problems occur
in a scientific context where there may be a continuous family of plausible data
generation processes associated to the presence of systematic uncertainties.
Robust inference is possible if it is based on a pivot -- a quantity whose
distribution does not depend on the unknown value of the nuisance parameters
that parametrize this family of data generation processes. In this work,  we
introduce and derive theoretical results for a training procedure based on
adversarial networks for enforcing the pivotal property (or, equivalently,
fairness with respect to continuous attributes) on a predictive model. The
method includes a hyperparameter to control the trade-off between accuracy and
robustness. We demonstrate the effectiveness of this approach with a toy example
and an examples from particle physics.

\end{abstract}

@@

In terms of applications, the proposed solution can be used in any situation
where the training data may not be representative of the real data the
predictive model will be applied to in practice. In the scientific context, the
presence of systematic uncertainty can be incorporated by considering a family
of data generation processes, and it would be worth revisiting those scientific problems
that utilize machine learning in light of this technique. Moreover, the approach
also extends to cases where independence of the predictive model with respect to
observed random variables is desired, as in domain adaptation or fairness in
classification (e.g. \cite{Shimmin:2017mfk}).
% not sure this is a great sentence to end with, sounds like a sales pitch
% Again, trying our algorithm on these use cases is certainly
%worth investigating.
